Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-09-24 GWLDCII.tex
read statements of proofs. added questions

  \begin{lem}\label{lem n-2 bad part 1}
Let $V$ and $W$ be as in Lemma~\ref{lem I}, and suppose that $n-2,n-1 \in I_{n-2}^{V}$. Then:
  \begin{enumerate}
  \item If $n-4 \not\in I_1^V\setminus I_n^V$, then $I_{n-2}^W$ contributes an $(n-3)\rightarrow (n-2)$ plus and an $(n-5)\rightarrow (n-1)$ plus, along with the one plus contributed by $I_n^V$.
  \item If $n-4 \in I_1^V\setminus I_n^V$, then $I_{n-2}^W$ contributes an $(n-3)\rightarrow (n-2)$ plus, an $(n-4)\rightarrow (n-1)$ plus and a $(n-5)\rightarrow (n)$ plus while $I_n^V$ contributed an $(n-4)\rightarrow (n)$ plus.
  \end{enumerate}
  \end{lem}

@@

We make one further simplification in order to eliminate the possibility that $n-2 \in I_{n-2}^V$ but $n-1 \not\in I_{n-2}^V$, which can only occur if our $W$ is in Case 2 of Figure~\ref{fig special p} and $n-1$ supports no propagators other than $p$. In this situation, apply the dihedral transformation that reflects $W$ along the line perpendicular to the $(n-2){th}$ edge, so that $p$ is unchanged but $q = (n-1,1)$ in the new diagram. The new diagram is an example of Case 1.

@@

  From Lemma~\ref{lem shape} we know how the shapes of the Le diagrams of $V$ and $W$ are related; let $\mathcal{A}$ and $\mathcal{B}$ be as described in that lemma and subsequent discussion.  Lemmas~\ref{lem n and n-1}, \ref{lem n-2 good}, and \ref{lem n-2 bad} tell us that the three boxes of the bottom row of the Le diagram of $W$ each have a plus.  We will use Lemmas~\ref{lem n and n-1} through \ref{lem other k} to construct a bijection between the plusses of the Le diagram of $V$ and the plusses of the Le diagram of $W$ that are not in the bottom row.  This bijection is defined as follows:
  \begin{itemize}
  \item All plusses from $\mathcal{B}$ for $V$ maintain their positions in $\mathcal{B}$ for $W$.
  \item All plusses from the leftmost two columns (the $n$ and the $n-1$ columns) of $\mathcal{A}$ for $V$ maintain their positions in $\mathcal{A}$ for $W$.
  \item If there is a plus in the $n-2$ column of $\mathcal{A}$ in $V$ then Lemma~\ref{lem n-2 bad} applies, so there is exactly one such plus.  If $n-4 \not\in I_1^V$ then map this plus to the $(n-5)\rightarrow (n-1)$ plus in $W$, whereas if $n-4 \in I_1^V$ then map it to the $(n-5) \rightarrow n$ plus in $W$.
  \item All plusses in the $n-3$ column for $V$ are shifted one square to the left in $\mathcal{A}$ for $W$, i.e. into the $n-2$ column.
  \end{itemize}
The majority of these points are clearly reversible and hence bijective; the only possible ambiguity is the third bullet point. In this case we are in the setting of Lemma~\ref{lem n-2 bad}. If $n-4 \not\in I_1^V$ there is no plus in the $(n-5) \rightarrow (n-1)$ position in $V$, whereas if $n-4 \in I_1^V$ then there is a plus in this position but no plus in the $(n-5)\rightarrow n$ position. In either case, per Lemma~\ref{lem n-2 bad} this is the only new plus in region $\mathcal{A}$ for $W$, so all plusses are accounted for and paired up uniquely with plusses in $V$.

>>>>

  \begin{lem}\label{lem n-2 bad part 1}
Let $V$ and $W$ be as in Lemma~\ref{lem I}, and suppose that $n-2,n-1 \in I_{n-2}^{V}$. Then:
  \begin{enumerate}
  \item If $n-4 \not\in I_1^V\setminus I_n^V$, then $I_{n-2}^W$ contributes an $(n-3)\rightarrow (n-2)$ plus and an $(n-5)\rightarrow (n-1)$ plus, along with \hlfix{the one}{check wording: 'the one' claims that $I_n^V$ only contributes one plus while 'one' claims that $I_{n-2}^W$ contributes one of the $I_n^V$ pluses} plus contributed by $I_n^V$.
  \item If $n-4 \in I_1^V\setminus I_n^V$, then $I_{n-2}^W$ contributes an $(n-3)\rightarrow (n-2)$ plus, an $(n-4)\rightarrow (n-1)$ plus and a $(n-5)\rightarrow (n)$ plus while $I_n^V$ contributed an $(n-4)\rightarrow (n)$ plus.
  \end{enumerate}
  \end{lem}

@@

We make one further simplification in order to eliminate the possibility that $n-2 \in I_{n-2}^V$ but $n-1 \not\in I_{n-2}^V$, which can only occur if our $W$ is in Case 2 of Figure~\ref{fig special p} and $n-1$ supports no propagators other than $p$. In this situation, apply the dihedral transformation that reflects $W$ along the line perpendicular to the $(n-2){th}$ edge, so that $p$ is unchanged but $q = (n-1,1)$ in the new diagram. The new diagram is an example of Case 1, {\color{violet} i.e. satisfying $n-2 \not \in I_{n-2}^V$}. \sanote{pull this simplification out ealier (before 4.10), so that when I'm counting cases, I'm not confused as to why this one hasn't been covered.}

@@

  From Lemma~\ref{lem shape} we know how the shapes of the Le diagrams of $V$ and $W$ are related; let $\mathcal{A}$ and $\mathcal{B}$ be as described in that lemma and subsequent discussion.  Lemmas~\ref{lem n and n-1}, \ref{lem n-2 good}, and \ref{lem n-2 bad} tell us that the three boxes of the bottom row of the Le diagram of $W$ each have a plus.  We will use Lemmas~\ref{lem n and n-1} through \ref{lem other k} to construct a bijection between the plusses of the Le diagram of $V$ and the plusses of the Le diagram of $W$ that are not in the bottom row.  This bijection is defined as follows:
  \begin{itemize}
  \item All plusses from $\mathcal{B}$ for $V$ maintain their positions in $\mathcal{B}$ for $W$.
  \item All plusses from the leftmost two columns (the $n$ and the $n-1$ columns) of $\mathcal{A}$ for $V$ maintain their positions in $\mathcal{A}$ for $W$.
  \item If there is a plus in the $n-2$ column of $\mathcal{A}$ in $V$ then Lemma~\ref{lem n-2 bad} applies, so there is exactly one such plus.  If $n-4 \not\in I_1^V$ then map this plus to the $(n-5)\rightarrow (n-1)$ plus in $W$, whereas if $n-4 \in I_1^V$ then map it to the $(n-5) \rightarrow n$ plus in $W$.
  \item All plusses in the $n-3$ column for $V$ are shifted one square to the left in $\mathcal{A}$ for $W$, i.e. into the $n-2$ column.
  \end{itemize}
The majority of these points are clearly reversible and hence bijective; the only possible ambiguity is the third bullet point. In this case we are in the setting of Lemma~\ref{lem n-2 bad}. If $n-4 \not\in I_1^V$ there is no plus in the $(n-5) \rightarrow (n-1)$ position in $V$, whereas if $n-4 \in I_1^V$ then there is a plus in this position but no plus in the $(n-5)\rightarrow n$ position. {\color{red} what about the arrow $(n-4)\rightarrow (n-1)$?} In either case, per Lemma~\ref{lem n-2 bad} this is the only new plus in region $\mathcal{A}$ for $W${\color{red} what about the arrows $(n-3)\rightarrow (n-2)$?}, so all plusses are accounted for and paired up uniquely with plusses in $V$.
